Boundary Labeling for annotated documents

### 2018-04-29 LaTeX/Paper.tex
Paper:Completed Section4, wrote Section 5 - Conclusion, added abstract. Program: No changes.

\setaddress{Scherzergasse 10/8, 1020 Wien}
\setregnumber{1125755}
\setdate{25}{09}{2017}%TODO: Update

@@

%\begin{abstract}
%\todo{Enter your text here.}
%\end{abstract}

@@

%Beispiele von suboptimalen Lösungen einfügen? (Bilder)
Boundary labeling in text documents however, is rarely discussed, and only few papers exist about this topic. The programs that employ this style of annotation often also use rather simple algorithms, to mediocre results or make extensive use of the interactivity of a digital medium, showing annotations only on demand. However, the few papers that approach this topic add interesting information to the discussion.

@@

\section{Drawing Area}
As this program is a proof of concept, the drawing area itself can't be interacted with, it only serves to display the algorithm's results. If we were to adapt this program for regular use, the user should be able to manually change routings or move labels around here.
Due to reasons described below in Section~\ref*{sec:Challenge}, each word has to be placed individually, which allows us to create the routing graph alongside the darwing process. 
After the text has been drawn completely, the routing algorithm is invoked from here, and its results are visualized.

@@

To generate data, we created our own texts using word length statistics from Table III in "Length-frequency statistics for written English" by Miller et al. \cite{Miller1958}, which lists word frequencies by length. We opted to use the data from the "Content Words" column, as the combined statistics almost exclusively produced words with three or less letters in our tests.
Using this data, we compiled our own fixed-length testing texts by creating words containing randomized alphabetic characters, taking care that the word length distribution matched our data.
A fixed number of annotation sites is inserted into the text either by distributing their locations uniformly across the text, or by clustering them regionally.

For the clustering approach, we divided the text vertically and horizontally into three subsections each - top/center/bottom and left/center/right respectively. To determine the site's location, we then determined the line the site will be in and its exact word by generating numbers from two normal distributions, each with a standard deviation of $1/6$th of the text's width or height, and a mean located at 25\%, 50\% or 75\% of that parameter, depending on the chosen region.

@@

Adding more sources to the text increases the both the space usage of the labeling area and the number of successful routes, but there seems to be a limit, as increasing the amount of sources only brings marginal improvements after a certain point. For our experiments, this was reached at 15 sources in a 300-word text. Doubling their amount improved both the space usage and the amount of routed leaders for several test instances, but the overall highest amount of successful routings increased only by 1, whereas the increase from 10 to 15 sources impacted the results much stronger. (See Fig.~\ref*{fig:uniformstats} for details.)

 \begin{figure}
 	\centering
 	\begin{subfigure}[b]{\textwidth}
 		\centering
 		\includegraphics[scale=0.8]{Rplot_10u.png}
 		\caption{\label{fig:10u}Results for 10 sources}
 	\end{subfigure}

 	\begin{subfigure}[b]{\textwidth}
 		\centering
 		\includegraphics[scale=0.8]{Rplot_15u.png}
 		\caption{\label{fig:15u}Results for 15 sources}
 	\end{subfigure}
    \begin{subfigure}[b]{\textwidth}
		 \centering
		 \includegraphics[scale=0.8]{Rplot_30u.png}
		 \caption{\label{fig:30u}Results for 30 sources}
    \end{subfigure}

@@

The effects of clustering are minor, and mostly outweighed by the influence of vertical placement, as the average word length is short enough that there is enough whitespace in each line to avoid leaders from blocking each other.
%Increasing the word length would make this effect more severe, and it would be interesting to see the influence on the results.

@@

@@

%Section Ideas: The Program/Framework (Modellerklärung), The Algorithm(s), Implementation, Evaluation, Conclusion

>>>>

\setaddress{Scherzergasse 10/8, 1020 Wien}
\setregnumber{1125755}
\setdate{29}{04}{2018}%TODO: Update

@@

\begin{abstract}
	In this paper, we present an algorithm capable of solving the one-sided boundary-labeling problem for crossing-free, monotonous OPO-Leaders in $O(n^2)$ using only the space between words and lines. We prove its correctness and evaluate its performance under different conditions.
\end{abstract}

@@

Boundary labeling in text documents however, is rarely discussed, and only few papers exist about this topic. The programs that employ this style of annotation often also use rather simple algorithms, to mediocre results or make extensive use of the interactivity of a digital medium, showing annotations only on demand. However, the few papers that approach this topic add interesting information to the discussion.

@@

\section{Drawing Area}
As this program is a proof of concept, the drawing area itself can't be interacted with, it only serves to display the algorithm's results. If we were to adapt this program for regular use, the user should be able to manually change routings or move labels around here.
Due to reasons described below in Section~\ref*{sec:Challenge}, each word has to be placed individually, which allows us to create the routing graph alongside the drawing process. 
After the text has been drawn completely, the routing algorithm is invoked from here, and its results are visualized.

@@

To generate data, we created our own texts using word length statistics from Table III in "Length-frequency statistics for written English" by Miller et al. \cite{Miller1958}, which lists word frequencies by length. We opted to use the data from the "Content Words" column, as the combined statistics almost exclusively produced words with three or less letters in our tests. \change{Furthermore, we created a custom distribution based on these values to test the algorithm's behavior in texts with longer words.}
Using this data, we compiled our own fixed-length testing texts by creating words containing randomized alphabetic characters, taking care that the word length distribution matched our data. \change{The results of both distributions can be seen in Fig.~\ref{fig:wordlength}}
A fixed number of annotation sites is inserted into the text either by distributing their locations uniformly across the text, or by clustering them regionally.

\begin{figure}
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[scale=0.65]{ContentWords.png}
		\caption{A generated text using the "Content Words" distribution from Miller et al.\cite{Miller1958}.}
	\end{subfigure}
	~\\
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[scale=0.65]{LongerWords.png}
		\caption{A generated text using our custom distribution.}
	\end{subfigure}
	\label{fig:wordlength}
	\caption{Results for both text generation distributions, with annotations.}
\end{figure}	
For the clustering approach, we divided the text vertically and horizontally into three subsections each - top/center/bottom and left/center/right respectively. To determine the site's location, we then determined the line the site will be in and its exact word by generating numbers from two normal distributions, each with a standard deviation of $1/6$th of the text's width or height, and a mean located at 25\%, 50\% or 75\% of that parameter, depending on the chosen region.

@@

Adding more sources to the text increases the both the space usage of the labeling area and the number of successful routes, but there seems to be a limit, as increasing the amount of sources only brings marginal improvements after a certain point. For our experiments, this was reached at 15 sources in a 300-word text. Doubling their amount improved both the space usage and the number of routed leaders for several test instances, but the overall highest amount of successful routings increased only by 1, whereas the increase from 10 to 15 sources impacted the results much stronger. (See Fig.~\ref*{fig:uniformstats} for details.)

 \begin{figure}
 	\centering
 	\begin{subfigure}[b]{\textwidth}
 		\centering
 		\includegraphics[scale=0.6]{Rplot_10u.png}
 		\caption{\label{fig:10u}Results for 10 sources}
 	\end{subfigure}

 	\begin{subfigure}[b]{\textwidth}
 		\centering
 		\includegraphics[scale=0.6]{Rplot_15u.png}
 		\caption{\label{fig:15u}Results for 15 sources}
 	\end{subfigure}
    \begin{subfigure}[b]{\textwidth}
		 \centering
		 \includegraphics[scale=0.6]{Rplot_30u.png}
		 \caption{\label{fig:30u}Results for 30 sources}
    \end{subfigure}

@@

The effects of clustering are minor, and mostly outweighed by the influence of vertical placement, as the average word length is short enough that there is sufficient whitespace in each line to avoid leaders from blocking each other.

\newpage
\change{Re-running the tests with an increased word length showed several changes: Most noticable was a higher variance in results - whereas the histogram in Fig.~\ref*{fig:15u} has a noticable peak at 10 successful routings, the values in Fig.~\ref*{fig:15uLong} are more spread out, reaching both better and worse end results.
The bottom left clustering also no longer achieves obviously better results than other vertex placements. While Fig.~\ref*{fig:15blLong} has less results with nine or less successful routings then Fig.~\ref*{fig:15uLong}, it also has less results in the 12+ range.
Finally, the vertical placement of vertices has a noticable impact - Fig.~\ref*{fig:15blLong} contains less results in below 10 successful routings than Fig.~\ref*{fig:15brLong}, and even has some instances with 13 successes.}

\begin{figure}
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[scale=0.6]{Rplot_15u_longer.png}
		\caption{\label{fig:15uLong}Results for uniform distribution.}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[scale=0.6]{Rplot_15bl_longer.png}
		\caption{\label{fig:15blLong}Results for clustered distribution in the bottom left.}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[scale=0.6]{Rplot_15br_longer.png}
		\caption{\label{fig:15brLong}Results for clustered distribution in the bottom right.}
	\end{subfigure}
	\caption{Test results for instances with 15 differently distributed sources over a 300-word text with increased word length.}
	\label{fig:longTests}
\end{figure}
%Increasing the word length would make this effect more severe, and it would be interesting to see the influence on the results.

@@

\change{In this paper we presented an algorithm capable of solving the one-sided boundary labeling problem for monotonous, crossing-free OPO-Leaders using only the whitespace between words and lines. We have shown it to run in $O(n^2)$ and proven its correctness. Finally, we have evaluated its performance under different conditions.}

@@

\change{An obvious weakness of our algorithm is its inability to create routings for source nodes above the next free annotation positions. Adding leaders that are only allowed to go down instead of up would allow for these positions to be routed, but would require extra precautions to avoid intersecting leaders. Alternatively, leaders could be restricted by how many P-Segments can be included before reaching the labeling area to make them easier to follow.}
